---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openjourney

![](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg)

The openjourney package allows to query trip durations between cooordinates within Switzerland. It wraps the [Open Journey Planer API](https://opentransportdata.swiss/de/cookbook/open-journey-planner-ojp/) provided by opentransportdata.swiss.

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("tlorusso/openjourney")
```

```{r setup}
library(openjourney)
library(tidyverse)
library(sf)
library(tidygeocoder)
library(xml2)
```

# Usage

## API-Token
To be able to query the API a token is needed. A public key is available in the [documentation](https://opentransportdata.swiss/de/cookbook/open-journey-planner-ojp/#Einleitung) which can be used for a limited number of queries. Private keys with higher rate limits can be created on opentransportdata.swiss.

In our example we'll use the public key.
```{r}
token1 <- paste("Bearer", "57c5dbbbf1fe4d000100001842c323fa9ff44fbba0b9b925f0c052d1", sep = " ")
```

## Query trip durations

Lets get some coordinates for some sample locations.
```{r}
# get coordinates of some locations
coords <- geo(address = c("Zürich Schwamendingerplatz, Switzerland",
                          "Zürich Stadelhofen, Switzerland",
                          "Uster Bahnhof, Switzerland",
                          "Bern Hauptbahnhof, Switzerland",
"Bahnhof Stettbach, Switzerland"),
method ='osm')
```

```{r eval=TRUE, echo=FALSE}

# extract coordinates 
coords_list <- coords %>% 
                select(long,lat) %>% 
                purrr::transpose()

# set coordinates of the origins
origins <- coords_list[c(1:4)]

# set coordinates of the desination
destinations <- coords_list[c(5)]

# set departure time
dep_time <-paste0(Sys.Date(),"T08:34:40")

# query the trip durations
trips <- get_tripduration(auth=token1,
                          origin=origins,
                          origin_id = coords$address[1:4],
                          destination=destinations,
                          destination_id=coords$address[5],
                          time=dep_time,
                          sys.sleep=5)
```

# Plot trip durations

```{r}
ggplot(trips, aes(duration_min,
                  paste0(origin_id, "\n - ", destination_id),
                  size=transfers))+
  geom_point()+
  theme_minimal()+
  scale_fill_viridis_c()+
  labs(y="")+
  scale_x_continuous(limits=c(0,100))
```

